---
title: Survey sample size simulation
author: Michael Flynn
date: "`r Sys.Date()`"
execute:
  echo: false
  message: false
  warning: false
format:
  html:
    toc: true
editor_options: 
  chunk_output_type: console
---

This document is intended to provide a basic Bayesian "power" analysis to help us understand the probability of detecting an effect as a function of the study's sample size.

## Setup

Here we load the packages used to simulate the data and run the analysis.
```{r setup}
# Load libraries
library(simstudy)
library(data.table)
library(tidyverse)
library(brms)
library(marginaleffects)
library(tidybayes)
library(ggdist)
library(arm)
library(fabricatr)
library(flynnprojects)

```


## Simulate base data

This first step will simulate the data we expect to collect in the survey. Currently the survey experiment has a total of four possible treatment groupings:

1. *Control*: This question asks respondents about their attitudes towards increasing the US military presence in Poland. 
2. *Treatment 1*: The first treatment group includes both mentions of Russia and mentions of economic benefits that flow from a US presence.
3. *Treatment 2*: The second treatment prompt only mentions the threat of Russian aggression.
4. *Treatment 3*: The third treatment prompt only mentions the possibility of economic benefits flowing from US military personnel deployed tot he host state.


```{r function-setup}

# So here I want to write a function that will do the following
# 1. Set the basic parameters that can vary (N, effect sizes)
# 2. Simulate the data based on this information
# 3. Run the mode.
# 4. Recover parameters and save them
# 5. Plot the accumulated parameters
power_sim <- function(N, Groups, iters, seed,
                      beta_p_1, beta_p_2, beta_p_3, beta_p_age, 
                      beta_n_1, beta_n_2, beta_n_3, beta_n_age,
                      beta_p_I, beta_n_I) {

# Set treatment labels
treatment_labels <- c("control", "t1", "t2", "t3")
  
#set seed for simulations  
set.seed(seed)
ITER <- 2000
WARM <- ITER/2
SEED <- seed
CORES <- 4

# Create data frame with nested list to store output of models
sims <- data.frame(N = rep(N, iters),
                   iters = rep(iters, iters),
                   data = rep(NA, iters))

for(i in 1:length(sims$data)) {

tempdata <- fabricate(
  treatment_group = add_level(
    N = Groups,
    label = treatment_labels
  ),
  individual = add_level(
    N = sims$N[i],
    age = round(runif(sims$N[i], 18, 80))
  )
) |> 
  mutate(control = ifelse(label == "control", 1, 0),
         t1 = ifelse(label == "t1", 1, 0),
         t2 = ifelse(label == "t2", 1, 0),
         t3 = ifelse(label == "t3", 1, 0),
         xb_pos = beta_p_I + beta_p_1 * t1 + beta_p_2 * t2 + beta_p_3 * t3 + beta_p_age * age,
         xb_neg = beta_n_I + beta_n_1 * t1 + beta_n_2 * t2 + beta_n_3 * t3 + beta_n_age * age,
         p_pos = plogis(xb_pos),
         p_neg = plogis(xb_neg),
         y_pos = rbinom(length(p_pos), 1, prob = p_pos),
         y_neg = rbinom(length(p_neg), 1, prob = p_neg),
         response = case_when(
           y_pos == 1 ~ "Positive",
           y_neg == 1 ~ "Negative",
           y_pos == 0 & y_neg == 0 ~ "Neutral",
           y_pos == 1 & y_neg == 1 & p_pos > p_neg ~ "Positive"
         ))


tempmod <- brm(response ~ factor(label) + age,
               data = tempdata,
               family = categorical(link = "logit",
                                    refcat = "Neutral"),
               iter = ITER,
               warmup = WARM,
               seed = SEED,
               cores = CORES,
               backend = "cmdstanr")

# I can't figure out how to nest the entire data frame without using the nest function here.
# Also adding the probability that a given value is above or below 0
samples <- as.data.frame(tidy_draws(tempmod)) |> 
  sample_draws(ndraws = 100) |> 
  mutate(across(starts_with("b_"),
                ~bayestestR::pd(.x),
                .names = "{col}_pd")) |> 
  mutate(SampleSize = sims$N[i]*4)

sims$data[i] <- nest(samples, data = everything())

}

# Un-nesting because keeping it nested imposes some overly complicated structures here that don't seem necessary.
sims <- unnest(sims, cols = "data") 

return(sims)

}


```



```{r test-run}
#| echo: false
#| message: false

Nlist <- c(50, 100, 150, 250)

powtest <- power_sim(N = Nlist,
                     Groups = 4,
                     iters = 100,
                     seed = 1234,
                     beta_p_1 = rnorm(1, 1.1, 0.2),
                     beta_p_2 = rnorm(1, 0.5, 0.2),
                     beta_p_3 = rnorm(1, 0.1, 0.2),
                     beta_n_1 = rnorm(1, -0.5, 0.2),
                     beta_n_2 = rnorm(1, -0.1, 0.2),
                     beta_n_3 = rnorm(1, -0.1, 0.2),
                     beta_p_age = rnorm(1, -0.02, 0.004),
                     beta_n_age = rnorm(1, +0.01, 0.004),
                     beta_p_I = rnorm(1, -1, 0.1),
                     beta_n_I = rnorm(1, -1, 0.1))

```


Now let's check some plots

```{r posterior-plots}

# First let's extract the data from the function and put it into a long format so it's easier to systematize the graphics
# 
powtest.df <- rbindlist(powtest$data, idcol = TRUE) |> 
  dplyr::select(.id, .chain, .iteration, .draw, SampleSize, ends_with("_pd"), starts_with("b_")) |> 
  melt(id.vars = c(".id", ".chain", ".iteration", ".draw", "SampleSize"),
       measure.vars = c(6:25)) |> 
  mutate(group = case_when(
    grepl(".*_pd.*", variable) ~ "Probability Direction",
    TRUE ~ "Effect"
  )) 

# Next let's make a plot of all of the coefficient values and the simulated posterior distributions for those variables
powtest.df |> 
  filter(group == "Effect") |>
  filter(grepl(".*control|t\\d.*", variable)) |>
  filter(SampleSize > 100) |> 
  ggplot(aes(x = value, group = .id)) +
  stat_slab(aes(color = stat(x > 0)),
            size = 0.3,
            fill = NA, 
            show_interval = FALSE) +
  facet_grid(SampleSize ~ variable) +
  theme_flynn() +
  scale_color_manual(values = c("#FFBD33" , "#1F1CFE")) +
  labs(x = "Coefficient",
       y = "Density",
       color = "Direction")

# Next let's look at the probability of finding the intended effect for each variable.
powtest.df |> 
  filter(group == "Probability Direction") |> 
  group_by(SampleSize, .id, variable) |>
  dplyr::summarise(mean = mean(value, na.rm = TRUE)) |> 
  group_by(SampleSize, variable) |> 
  dplyr::summarise(prop = sum(mean >= 0.95) / length(.id)) |> 
  ungroup() |> 
  ggplot(aes(x = SampleSize, y = prop, color = stat(y > 0.95))) +
    geom_line() +
  geom_point() +
  theme_flynn() +
  facet_wrap(~ variable, ncol = 3) +
  scale_color_manual(values = c("#FFBD33" , "#1F1CFE")) +
  labs(x = "Sample Size",
       y = "Proportion",
       color = "Detection in > 95% of Models")
  

```
