---
title: Survey sample size simulation
author: Michael Flynn
date: "`r Sys.Date()`"
execute:
  echo: false
  message: false
  warning: false
format:
  html:
    toc: true
editor_options: 
  chunk_output_type: console
---

This document is intended to provide a basic Bayesian "power" analysis to help us understand the probability of detecting an effect as a function of the study's sample size.

## Setup

Here we load the packages used to simulate the data and run the analysis.
```{r setup}
# Load libraries
library(simstudy)
library(data.table)
library(tidyverse)
library(brms)
library(marginaleffects)
library(tidybayes)
library(ggdist)
library(arm)
library(fabricatr)
library(flynnprojects)
library(job)
library(tictoc)
```


## Simulate base data

This first step will simulate the data we expect to collect in the survey. Currently the survey experiment has a total of four possible treatment groupings:

1. *Control*: This question asks respondents about their attitudes towards increasing the US military presence in Poland. 
2. *Treatment 1*: The first treatment group includes both mentions of Russia and mentions of economic benefits that flow from a US presence.
3. *Treatment 2*: The second treatment prompt only mentions the threat of Russian aggression.
4. *Treatment 3*: The third treatment prompt only mentions the possibility of economic benefits flowing from US military personnel deployed tot he host state.

Additionally we will adjust for the following predictor variables in the model:

1. Contact
2. Benefits
3. Age
4. Income
5. Gender
6. Minority
7. Religion
8. Education
9. Ideology


```{r function-setup}

# So here I want to write a function that will do the following
# 1. Set the basic parameters that can vary (N, effect sizes)
# 2. Simulate the data based on this information
# 3. Run the mode.
# 4. Recover parameters and save them
# 5. Plot the accumulated parameters
power_sim <- function(N, iters, seed,
                      beta_p_1, 
                      beta_p_2, 
                      beta_p_3, 
                      beta_p_age_2, beta_p_age_3, beta_p_age_4, beta_p_age_5, beta_p_age_6, 
                      beta_p_contact, 
                      beta_p_benefits, 
                      beta_p_income_1, beta_p_income_2, beta_p_income_3, beta_p_income_4, 
                      beta_p_gender, 
                      beta_p_minority, 
                      beta_p_ed, 
                      beta_p_id,
                      beta_n_1, beta_n_2, beta_n_3, 
                      beta_n_age_2, beta_n_age_3, beta_n_age_4, beta_n_age_5, beta_n_age_6, 
                      beta_n_contact, 
                      beta_n_benefits, 
                      beta_n_income_1, beta_n_income_2, beta_n_income_3, beta_n_income_4, 
                      beta_n_gender, 
                      beta_n_minority, 
                      beta_n_ed, 
                      beta_n_id, 
                      beta_p_I, 
                      beta_n_I, 
                      I_error) {

# Set seed
set.seed(seed)

# Set treatment labels
treatment_labels <- c("control", "t1", "t2", "t3")


#set seed and arguments for brms models  
ITER <- 2000
WARM <- ITER/2
SEED <- seed
CORES <- 8
CHAINS <- 4

PRIORS <- prior(normal(0, 0.2), class = b)

# Create data frame with nested list to store output of models
sims <- data.frame(N = rep(N, iters),
                   iters = rep(iters, iters),
                   data = rep(NA, iters))

# We want the error for each province to be fixed and not vary/flip between simulations. There can still be a distribution around each error though, so long as it's mean stays mostly the same in a positive/negative position.
provincelist <- data.table::fread("Data/district-list.txt") |>
  group_by(province) |>
  mutate(error = round(I_error, 3))


for(i in 1:length(sims$data)) {

  
# Set arguments for sample size and group sizes
N_total <- sims$N[i]
N_groups <- n_distinct(provincelist$province)
N_pergroup <- sims$N[i]/N_groups
  
tempdata <- fabricate(
  province = add_level(
    N = N_groups,
    label = unique(provincelist$province),
    error = unique(provincelist$error)
  ),
  individual = add_level(
    N = N_pergroup
  )
) |>
  mutate(age = sample(c("Age 18-24", "Age 25-34", "Age 35-44", "Age 45-54", "Age 55-64", "Age 65+"), replace = TRUE, N_total),
         contact_pers = rbinom(N_total, 1, 0.12),
         benefit_pers = rbinom(N_total, 1, 0.09),
         income = sample(c(1, 2, 3, 4, 5), replace = TRUE, N_total),
         gender = rbinom(N_total, 1, 0.50),
         minority = rbinom(N_total, 1, 0.13),
         education = round(rnorm(N_total, 14.5, 3.7)),
         ideology = round(rnorm(N_total, 5.8, 2.5)),
         treatment = sample(treatment_labels,
                            replace = TRUE,
                            N_total),
         control = ifelse(treatment == "control", 1, 0),
         t1 = ifelse(treatment == "t1", 1, 0),
         t2 = ifelse(treatment == "t2", 1, 0),
         t3 = ifelse(treatment == "t3", 1, 0),
         age_1 = ifelse(age == "Age 18-24", 1, 0),
         age_2 = ifelse(age == "Age 25-34", 1, 0),
         age_3 = ifelse(age == "Age 35-44", 1, 0),
         age_4 = ifelse(age == "Age 45-54", 1, 0),
         age_5 = ifelse(age == "Age 55-64", 1, 0),
         age_6 = ifelse(age == "Age 65+", 1, 0),
         age = factor(age, levels = c("Age 18-24", "Age 25-34", "Age 35-44", "Age 45-54", "Age 55-64", "Age 65+")),
         age = relevel(age, ref = 1),
         income_1 = ifelse(income == 1, 1, 0),
         income_2 = ifelse(income == 2, 1, 0),
         income_3 = ifelse(income == 3, 1, 0),
         income_4 = ifelse(income == 4, 1, 0),
         treatment = factor(treatment),
         income = factor(income),
         xb_pos = beta_p_I + error + beta_p_1 * t1 + beta_p_2 * t2 + beta_p_3 * t3 + beta_p_age_2 * age_2 + beta_p_age_3 * age_3 + beta_p_age_4 * age_3 + beta_p_age_5 * age_5 + beta_p_age_6 * age_6 + beta_p_income_1 * income_1 + beta_p_income_2 * income_2 + beta_p_income_3 * income_3 + beta_p_income_4 * income_4 + beta_p_contact * contact_pers + beta_p_benefits * benefit_pers + beta_p_gender * gender + beta_p_minority * minority + beta_p_ed * education + beta_p_id * ideology,
         xb_neg = beta_n_I + error + beta_n_1 * t1 + beta_n_2 * t2 + beta_n_3 * t3 + beta_n_age_2 * age_2 + beta_n_age_3 * age_3 + beta_n_age_4 * age_4 + beta_n_age_5 * age_5 + beta_n_age_6 * age_6 + beta_n_income_1 * income_1 + beta_n_income_2 * income_2 + beta_n_income_3 * income_3 + beta_n_income_4 * income_4 + beta_n_contact * contact_pers + beta_n_benefits * benefit_pers + beta_n_gender * gender + beta_n_minority * minority + beta_n_ed * education + beta_n_id * ideology,
         p_pos = plogis(xb_pos),
         p_neg = plogis(xb_neg),
         y_pos = rbinom(length(p_pos), 1, prob = p_pos),
         y_neg = rbinom(length(p_neg), 1, prob = p_neg),
         response = case_when(
           y_pos == 1 ~ "Positive",
           y_neg == 1 ~ "Negative",
           y_pos == 0 & y_neg == 0 ~ "Neutral",
           y_pos == 1 & y_neg == 1 & p_pos > p_neg ~ "Positive",
           y_pos == 1 & y_neg == 1 & p_pos < p_neg ~ "Negative",
           TRUE ~ "Neutral"
         ))


tempmod <- brms::brm(response ~ treatment + contact_pers + benefit_pers + income + minority + gender + age + ideology + education + (1 | province),
               data = tempdata,
               family = categorical(link = "logit",
                                    refcat = "Neutral"),
               prior = PRIORS,
               iter = ITER,
               warmup = WARM,
               seed = SEED,
               cores = CORES,
               chains = CHAINS,
               backend = "cmdstanr",
               control = list(max_treedepth = 12,
                              adapt_delta = 0.8),
               threads = threading(4))

# I can't figure out how to nest the entire data frame without using the nest function here.
# Also adding the probability that a given value is above or below 0
samples <- as.data.frame(tidy_draws(tempmod)) |> 
  sample_draws(ndraws = 100) |> 
  mutate(across(starts_with("b_"),
                ~bayestestR::pd(.x),
                .names = "{col}_pd")) |> 
  mutate(SampleSize = sims$N[i])

sims$data[i] <- nest(samples, data = everything())

}

# Un-nesting because keeping it nested imposes some overly complicated structures here that don't seem necessary.
sims <- unnest(sims, cols = "data") 

return(sims)

}


```



```{r test-run}
#| echo: false
#| message: false

tic()

# Note that Nlist provides the N for the individual treatment groups. The total sample size is N & 4. This is a function of how fabricatr structures data.
# Must use multiples of 16 since that's how many groups/provinces there are in the data
Nlist <- c(1600, 1920, 2560, 3040, 6000)

# First runt he function to simulate the results,
powtest <- power_sim(N = Nlist,
                     iters = 50,
                     seed = 3353,
                     beta_p_1 = rnorm(1, 1.0, 0.0),
                     beta_p_2 = rnorm(1, 0.5, 0.0),
                     beta_p_3 = rnorm(1, 0.1, 0.0),
                     beta_p_age_2 = rnorm(1, -0.12, 0.0), 
                     beta_p_age_3 = rnorm(1, -0.09, 0.0), 
                     beta_p_age_4 = rnorm(1, -0.05, 0.0), 
                     beta_p_age_5 = rnorm(1, 0.11, 0.0), 
                     beta_p_age_6 = rnorm(1, 0.19, 0.0), 
                     beta_p_contact = rnorm(1, 0.52, 0.0), 
                     beta_p_benefits = rnorm(1, 0.04, 0.0), 
                     beta_p_income_1 = rnorm(1, -0.03, 0.0), 
                     beta_p_income_2 = rnorm(1, 0.02, 0.0), 
                     beta_p_income_3 = rnorm(1, 0.002, 0.0), 
                     beta_p_income_4 = rnorm(1, 0.08, 0.0), 
                     beta_p_gender = rnorm(1, 0.8, 0.0), 
                     beta_p_minority = rnorm(1, -0.03, 0.0), 
                     beta_p_ed = rnorm(1, 0.03, 0.0), 
                     beta_p_id = rnorm(1, 0.39, 0.0),
                     beta_n_1 = rnorm(1, -0.9, 0.0), 
                     beta_n_2 = rnorm(1, -0.2, 0.0), 
                     beta_n_3 = rnorm(1, -0.5, 0.0), 
                     beta_n_age_2 = rnorm(1, 0.09, 0.0), 
                     beta_n_age_3 = rnorm(1, -0.01, 0.0), 
                     beta_n_age_4 = rnorm(1, -0.10, 0.0), 
                     beta_n_age_5 = rnorm(1, -0.18, 0.0), 
                     beta_n_age_6 = rnorm(1, -0.06, 0.0), 
                     beta_n_contact = rnorm(1, 0.18, 0.0), 
                     beta_n_benefits = rnorm(1, -0.42, 0.0), 
                     beta_n_income_1 = rnorm(1, -0.06, 0.0), 
                     beta_n_income_2 = rnorm(1, 0.01, 0.0), 
                     beta_n_income_3 = rnorm(1, -0.03, 0.0), 
                     beta_n_income_4 = rnorm(1, 0.04, 0.0), 
                     beta_n_gender = rnorm(1, 0.02, 0.0), 
                     beta_n_minority = rnorm(1, 0.06, 0.0), 
                     beta_n_ed = rnorm(1, 0.16, 0.0), 
                     beta_n_id = rnorm(1, -0.24, 0.0), 
                     beta_p_I = rnorm(1, -2.0, 0.0), 
                     beta_n_I = rnorm(1, -0.5, 0.0), 
                     I_error = rnorm(1, 0, 0.0))


# Next let's extract the data from the function and put it into a long format so it's easier to systematize the graphics
# 
powtest.df <- rbindlist(powtest$data, idcol = TRUE) |> 
  dplyr::select(.id, .chain, .iteration, .draw, SampleSize, ends_with("_pd"), starts_with("b_")) |> 
  melt(id.vars = c(".id", ".chain", ".iteration", ".draw", "SampleSize"),
       measure.vars = c(6:81)) |> 
  mutate(group = case_when(
    grepl(".*_pd.*", variable) ~ "Probability Direction",
    TRUE ~ "Effect"
  )) 


# Let's save the data so we can access it later
readr::write_csv(powtest.df, file = here::here("Data/power-sims.csv"))

toc()
```


Now let's check some plots

```{r posterior-plots}



# Next let's make a plot of all of the coefficient values and the simulated posterior distributions for those variables
test <- powtest.df |> 
  filter(group == "Effect") |>
  filter(grepl(".*treatment.*", variable)) |>
  ggplot(aes(x = value, group = .id)) +
  stat_slab(aes(color = stat(x > 0)),
            size = 0.3,
            fill = NA, 
            show_interval = FALSE) +
  geom_vline(xintercept = 0, size = 1.2) +
  facet_grid(SampleSize ~ variable) +
  theme_flynn() +
  scale_color_manual(values = c("#FFBD33" , "#1F1CFE")) +
  labs(x = "Coefficient",
       y = "Density",
       color = "Direction")

ggsave(here::here("Figures/fig-sim-spaghetti.jpg"), height = 7, width = 14, units = "in")

# Next let's look at the probability of finding the intended effect for each variable.
powtest.df |> 
  filter(group == "Probability Direction") |> 
  filter(grepl(".*treatment|t\\d.*", variable)) |>
  group_by(SampleSize, .id, variable) |>
  dplyr::summarise(mean = mean(value, na.rm = TRUE)) |> 
  group_by(SampleSize, variable) |> 
  dplyr::summarise(prop = sum(mean >= 0.8) / length(.id)) |> 
  ungroup() |> 
  ggplot(aes(x = SampleSize, y = prop, color = stat(y > 0.95))) +
    geom_line() +
  geom_point() +
  theme_flynn() +
  facet_wrap(~ variable, ncol = 3) +
  scale_color_manual(values = c("#FFBD33" , "#1F1CFE")) +
  labs(x = "Sample Size",
       y = "Proportion",
       color = "Detection in > 80% of Models")
  
ggsave(here::here("Figures/fig-sim-threshold.jpg"), height = 7, width = 12, units = "in")

```
